On the combination of Set Functions and Failures

### 2014-10-14 docs/src/extensions.tex
Manual extended and some typos fixed

\subsection{Narrowing on Int Literals}
In addition to narrowing on algebraic data types,
\CYS alos implements narrowing on values of the primitive type \code{Int}.
For example, the goal \code{x == 3 where x free}
can be narrowed to the solutions
\begin{curry}
Prelude> x == 3 where x free
{x = (-_x2)       } False
{x = 0            } False
{x = 1            } False
{x = (2 * _x3)    } False
{x = 3            } True
{x = (4 * _x4 + 1)} False
{x = (4 * _x4 + 3)} False
\end{curry}
Note that the free variables occuring in the binding are restricted to
positive numbers greater than $0$
(the output has been indented to increase readability).
This feature is realized by an internal binary representation
of integer numbers. If necessary, this representation can be exposed to
the user by setting the flag \code{BinaryInt} during installation:
\begin{curry}
make [kernel|install] RUNTIMEFLAGS=BinaryInt
\end{curry}
In an experimental (local) installation, the flag can also be set in the
interpreter:
\begin{curry}
:set ghc -DBinaryInt
\end{curry}
The example above will then be evaluated (without indentation) to:
\begin{curry}
Prelude> x == 3 where x free
{x = (Neg _x2)        } False
{x = 0                } False
{x = 1                } False
{x = (Pos (O _x3))    } False
{x = 3                } True
{x = (Pos (I (O _x4)))} False
{x = (Pos (I (I _x4)))} False
\end{curry}
In this output, values without free variables are presented like before.
For value containing a free variable,
the constructors \code{Neg} and \code{Pos} denote negative and
positive numbers (without $0$), while the constructors \code{O} and \code{I}
denote a $0$-- and $1$--bit where the \emph{least significant bit comes first}.
That is,
$\code{(Pos (I (O _x4)))} = +\code{(I (O _x4))} = + (2 * \code{(O _x4)}) + 1 = + (4 * \code{_x4}) + 1$
which meets the output above.

@@

>>>>

\subsection{Narrowing on Int Literals}

In addition to narrowing on algebraic data types,
\CYS also implements narrowing on values of the primitive type \code{Int}.
For example, the goal \ccode{x == 3 where x free}
is evaluated to the solutions
\begin{curry}
Prelude> x == 3 where x free
{x = (-_x2)       } False
{x = 0            } False
{x = 1            } False
{x = (2 * _x3)    } False
{x = 3            } True
{x = (4 * _x4 + 1)} False
{x = (4 * _x4 + 3)} False
\end{curry}
Note that the free variables occuring in the binding are restricted to
positive numbers greater than $0$
(the output has been indented to increase readability).
This feature is implemented by an internal binary representation
of integer numbers. If necessary, this representation can be exposed to
the user by setting the flag \code{BinaryInt} during installation:
\begin{curry}
make [kernel|install] RUNTIMEFLAGS=BinaryInt
\end{curry}
In an experimental (local) installation, the flag can also be set in the
interpreter:
\begin{curry}
:set ghc -DBinaryInt
\end{curry}
The example above will then be evaluated (without indentation) to:
\begin{curry}
Prelude> x == 3 where x free
{x = (Neg _x2)        } False
{x = 0                } False
{x = 1                } False
{x = (Pos (O _x3))    } False
{x = 3                } True
{x = (Pos (I (O _x4)))} False
{x = (Pos (I (I _x4)))} False
\end{curry}
In this output, values without free variables are presented as before.
For values containing a free variable,
the constructors \code{Neg} and \code{Pos} denote negative and
positive numbers (without $0$), while the constructors \code{O} and \code{I}
denote a $0$-- and $1$--bit where the \emph{least significant bit comes first}.
That is,
$\code{(Pos (I (O _x4)))} = +\code{(I (O _x4))} = + (2 * \code{(O _x4)}) + 1 = + (4 * \code{_x4}) + 1$
which meets the output above.

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "manual"
%%% End:

### 2014-10-14 docs/src/usage.tex
Manual extended and some typos fixed

>>>>

\subsection{Using \CYS in Batch Mode}

Although \CYS is primarily designed as an interactive system,
it can also be used to process data in batch mode.
For example, consider a Curry program, say \code{myprocessor}, that
reads argument strings from the command line and processes them.
Suppose the entry point is a function called \code{just_doit}
that takes no arguments. Such a processor can be invoked from
the shell as follows:
\begin{curry}
> kics2 :set args string1 string2 :load myprocessor.curry :eval just_doit :quit
\end{curry}
The \ccode{:quit} directive in necessary to avoid \CYS going
into interactive mode after the
excution of the expression being evaluated.
The actual run-time arguments (\code{string1}, \code{string2})
are defined by setting the option \code{args} (see above).

Here is an example to use \CYS in this way:
\begin{curry}
> kics2 :set args Hello World :add System :eval "getArgs >>= putStrLn . unwords" :quit
Hello World
>
\end{curry}
